Field-informed Reinforcement Learning of Collective Tasks with Graph Neural Networks

### 2023-05-20 paper.tex
tweaks

\usepackage{cleveref}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning Collective Tasks with Graph Neural Networks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

In this paper, we propose a novel hybrid approach that combines manual and automatic design of distributed controllers.
This follows a novel trend in which high-level declarative programming languages are mixed with machine learning techniques in order to synthesise robust collective controllers~\cite{DBLP:conf/acsos/Aguzzi21,DBLP:conf/icdcs/AguzziCV22,DBLP:conf/coordination/AguzziCV22}.
Specifically, we propose a solution called \ac{FIRL} that utilises aggregate computing~\cite{Beal2015Computer} together with a \ac{GNN}~\cite{Zhou2020AIOpen} in combination with a reinforcement learning approach, namely \ac{DQN}~\cite{mnih2015human}. 
% First, aggregate computing is utilised to collect information from neighbours and create a local knowledge base for each agent. Second, we utilise a \ac{GNN} within the \ac{DQN}. 
 Here the \ac{GNN} is trained on field-information from aggregate computing and provides so-called node embeddings for each agent, serving as input for the \ac{DQN}. 
 The \ac{DQN} provides then the appropriate actions for the agent to achieve their tasks.
%We further combine this with reinforcement learning techniques to respond to changing conditions in the environment. 
%
The main contribution of \ac{FIRL} is that it allows us to create distributed controllers that are informed by a collective knowledge that has been distilled during training, but that use only local information when deployed. This way, \ac{FIRL} can achieve a balance between manual design and automatic design, combining the benefits of both approaches while mitigating their drawbacks.
Moreover, the learned policies have the potential to scale to different network topologies due to the inherent nature of GNNs and aggregate computations.
%% Perhaps to much detail 
\ac{FIRL} can also be seen as a way of bridging the gap between symbolic and sub-symbolic AI methods, by integrating declarative programming with deep learning.
%
Conceptually, \ac{FIRL} leverages the ideas of \emph{behaviour implicit communication} \cite{DBLP:journals/ijaci/CastelfranchiPT10} \cite{DBLP:conf/e4mas/TummoliniCRVO04}, whereby intelligent agents (here trained by DQN) achieve collective goals by learning how to use signs they left in the environment (here made of fields): much like ants collectively rely on pheromones they produce \cite{DBLP:journals/anor/Parunak97}.

@@

 where agents exploit the field as a stigmergic medium to receive system-wide information and apply reasoning to this data.

>>>>

\usepackage{cleveref}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning of Collective Tasks with Graph Neural Networks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

In this paper, we propose a novel hybrid approach that combines manual and automatic design of distributed controllers.
This follows a novel trend in which high-level declarative programming languages are mixed with machine learning techniques in order to synthesise robust collective controllers~\cite{DBLP:conf/acsos/Aguzzi21,DBLP:conf/icdcs/AguzziCV22,DBLP:conf/coordination/AguzziCV22}.
Specifically, we propose a solution called \ac{FIRL} that utilises aggregate computing~\cite{Beal2015Computer} together with a \ac{GNN}~\cite{Zhou2020AIOpen} in combination with a reinforcement learning approach, namely \ac{DQN}~\cite{mnih2015human}. 
% First, aggregate computing is utilised to collect information from neighbours and create a local knowledge base for each agent. Second, we utilise a \ac{GNN} within the \ac{DQN}. 
 Here the \ac{GNN} is trained on field-information from aggregate computing and provides so-called node embeddings for each agent, serving as input for the \ac{DQN}. 
 The \ac{DQN} provides then the appropriate actions for the agent to achieve their tasks.
%We further combine this with reinforcement learning techniques to respond to changing conditions in the environment. 
%
The main contribution of \ac{FIRL} is that it allows us to create distributed controllers that are informed by a collective knowledge that has been distilled during training, but that use only local information when deployed. This way, \ac{FIRL} can achieve a balance between manual design and automatic design, combining the benefits of both approaches while mitigating their drawbacks.
Moreover, the learned policies have the potential to scale with size and adapt to different network topologies due to the inherent nature of GNNs and aggregate computations.
%% Perhaps to much detail 
\ac{FIRL} can also be seen as a way of bridging the gap between symbolic and sub-symbolic AI methods, by integrating declarative programming with deep learning.
%
Conceptually, \ac{FIRL} leverages the ideas of \emph{behaviour implicit communication} \cite{DBLP:journals/ijaci/CastelfranchiPT10} \cite{DBLP:conf/e4mas/TummoliniCRVO04}, whereby intelligent agents (here trained by DQN) achieve collective goals by learning how to use signs they left in the environment (here made of fields): much like ants collectively rely on pheromones they produce \cite{DBLP:journals/anor/Parunak97}.

@@

 where agents construct and exploit the field as a ``digital sign'' \cite{DBLP:journals/ijaci/CastelfranchiPT10} to receive system-wide information and apply reasoning to this data.
